### 2018-03-29 paper/sexSelectionSpacing-ver1.tex
Minor edits

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
\setcounter{subfigure}{1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{
Survival curves conditional on progression to next birth for urban women with eight or
more years of education; start point is nine months after prior birth
}
\label{fig:pps_high}
\end{figure}

@@

The results here also lead to a set of broader questions that
future research should address.
First, to what extent are the improvements in health for girls
relative to boys the result of selection, longer spacing between
births, or changing son preference?
There is some early evidence that selection make it appear that
girls are healthier, even though the real cause is a combination
of sex selection and higher mortality together with recall error \citep{Portner2018a}. 
Understanding what role these factors play in better health for
girls is especially important when evaluating policies that 
aim to directly limit the use of sex selection rather than 
changing preferences or incentives.

Second, we need to understand how female labor force participation
interact with the use of sex selection.
Increased autonomy for women, through, for example, better opportunities
for working outside the home, has been suggested as a way to increase
women's status and thereby lowering the use of sex selection \citep{Das-Gupta2016}.
This may, however, be a double-edged sword.
On the one hand, it is an obvious benefit to women who gain  
bargaining power and it also increases the cost of repeated 
sex-selective abortions.
On the other hand, it may further lower desired fertility, and 
everything else equal, that may lead to higher use of sex selection.
Understanding the trade-off between long-term benefits from improvements in
women's labor force participation and short-term costs from potential 
increases in sex selection is of paramount importance.

>>>>

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
\setcounter{subfigure}{1}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[2005--2016]{
    \begin{minipage}{0.46\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{
Survival curves conditional on progression to next birth for urban women with eight or
more years of education; start point is nine months after prior birth
}
\label{fig:pps_high}
\end{figure}

@@

The results here also lead to a set of broader questions that
future research should address.
First, to what extent are the improvements in health for girls
relative to boys the result of selection, the longer spacing between
births, or changing son preference?
There is some early evidence that selection makes it appear that
girls are healthier, even though the real cause is a combination
of sex selection and higher mortality together with recall error \citep{Portner2018a}. 
Understanding what role these factors play in better health for
girls is especially important when evaluating policies that 
aim to directly limit the use of sex selection rather than 
changing preferences or incentives.

Second, we need to understand how female labor force participation
interacts with the use of sex selection.
Increased autonomy for women, arising from, for example, better opportunities
for working outside the home, has been suggested as a way to increase
women's status and thereby lower the use of sex selection \citep{Das-Gupta2016}.
This may, however, be a double-edged sword.
On the one hand, it is an clear benefit to women who gain  
bargaining power, and it also increases the cost of repeated 
sex-selective abortions.
On the other hand, it may further lower desired fertility, and 
everything else equal, that may lead to higher use of sex selection.
Understanding the trade-off between long-term benefits from improvements in
women's labor force participation and short-term costs from potential 
increases in sex selection is of paramount importance.
